Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-07 doc/manuscript/manuscript.Rmd
Add broad section for Genetic Diversity
Add description of MLG-MCG correlation

>>>>

### Correlating Multilocus Genotypes with Mycelial Compatibility Groups {-}

We wanted to assess if there was any correlation between multilocus genotypes (MLG) and mycelial compatibility groups (MCG). 
This was done using a graph-based approach with community analysis.
We first created a contingency table with MLGs and MCGs and converted it to a directed and weighted edgelist where each edge was a connection from an MCG to an MLG weighted by the number of samples shared in the connection. 
The cluster walktrap community detection algorithm as implemented in the `cluster_walktrap()` function in *igraph* version 1.0.1 was used to define clusters of MLGs and MCGs [@csardi2006igraph, @pons2006computing].
All communities that had fewer than 10 members were then consolidated into one.
These community definitions was then used to assess the average genetic distance (as defined by Bruvo's distance) within members of the community [@bruvo2004simple].

## Genetic Diversity
